&nbsp;

### 2025-02-17 inst/app/www/about.Rmd

@@

The design of the app was done by Zsuzsa Szekely [(@szekely_Zsuzsa)](<https://twitter.com/szekely_zsuzsa>).

@@

If you have any questions or comments please write to Marton Kovacs to the following email address: [marton.balazs.kovacs@gmail.com](mailto:marton.balazs.kovacs@gmail.com)

>>>>

### Publications

The sample size calculations for the t-tests are presented in a tutorial paper: [Kovacs, van Ravenzwaaij, Hoekstra & Aczel (2022)](https://doi.org/10.1177/25152459211054059)

@@

The design of the app was done by Zsuzsa Szekely [(\@szekely_Zsuzsa)](https://twitter.com/szekely_zsuzsa).

@@

If you have any questions or comments please write to Marton Kovacs to the following email address: [marton.balazs.kovacs\@gmail.com](mailto:marton.balazs.kovacs@gmail.com)
